Community Analysis

### 2022-04-08 R/01-process-flux.Rmd
update analysis scripts

```{r plot_fluxes, fig.height=50}
flux_data %>%
 ggplot(aes(days, ppm)) +
 facet_grid(passage + treat ~ rep, scales = "free") +
 geom_point() +
 stat_smooth(method = 'lm', formula = y ~ x)
```

>>>>

```{r plot_fluxes, fig.height=20}
flux_data %>%
 ggplot(aes(days, ppm)) +
 facet_grid(flux_date + treat ~ rep, scales = "free") +
 geom_point() +
 stat_smooth(method = 'lm', formula = y ~ x)
```

### 2022-04-08 R/08-community.Rmd
update analysis scripts

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir=normalizePath('../'))
```

@@

source('R/functions.R')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir=normalizePath('../'))

@@

source('R/functions.R')
